Reliable Inferences from Simply Parameterised Models

### 2012-08-08 ms.tex
SOmething or other

\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\parindent=0cm

@@

\section{Example: Fitting an Emission Line}
Throughout this paper we will use a simple example of fitting an emission line
to noisy data in order to estimate the total flux of the line.

>>>>

\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\parindent=0cm
\newcommand{\yy}{\mathbf{y}}

@@

\section{Example 1: Fitting an Emission Line}
Throughout this paper we will use a simple example of fitting an emission line
to noisy data in order to estimate the total flux of the line.

\subsection{The Simply-Parameterised Model}
The model for the shape of the line is:
\begin{eqnarray}
\mathcal{M}(x; A, c, w) &=&
A\exp
\left[
-\frac{1}{2w^2}
\left(x - c\right)^2
\right]
\end{eqnarray}
where $A$ is the peak amplitude, $c$ is the central position of the line
and $w$ is the line width. To infer the parameters $\{A, c, w\}$ from some data
$\yy$, we will use Bayes' rule:
\begin{eqnarray}
p(A, c, w | \yy) \propto p(A, c, w)p(\yy | A, c, w).
\end{eqnarray}
To proceed, we just need to define the prior and the sampling distribution.

\subsection{The Sampling Distribution}
We will assume that the data are simply noisy measurements of the true line shape
$\mathcal{M}(x)$ at a finite number of $x$-values.
The sampling distribution, aka the probability distribution for the data $\yy$ given
the parameters, is simply a normal/gaussian distribution. Note that the
gaussian error assumption should be distinguished from the assumption of a gaussian
shape for the emission line.

\begin{eqnarray}
p(\yy|A, c, w) &=& \prod_{i=1}^N
\frac{1}{\sigma\sqrt{2\pi}}
\exp
\left[
-\frac{1}{2\sigma^2}\left(y_i - \mathcal{M}(x_i; A, c, w)\right)^2
\right].
\end{eqnarray}
